%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer \quad\textbar\quad Agentic Systems Design} % Job title
    {Infineon} % Organization
    {Bucharest, Romania} % Location
    {Oct. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Developing an AI chatbot based on ReAct agents}, used to speed up interaction to various data sources, as well as allow users to perform light tasks on queried data, such as plotting.}
        \item {\textbf{Improved chatbot explainability} by showing the user what its reasoning is, so that the user can adjust their prompts}
        \item {\textbf{Developed common framework} for all chatbot usecases, so that development doesn’t need to be repeated for each client}
      \end{cvitems}
    }

%---------------------------------------------------    ------
  \cventry
    {Software Engineer \quad\textbar\quad Methodology Research} % Job title
    {Amadeus Data Processing GmbH} % Organization
    {Munich, Germany} % Location
    {May 2023 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a global team to \textbf{deliver a tool for measuring software carbon emissions} that could be used by teams company-wide and syncing with the open-source Impact Framework to use their tool for computations.}
        \item {Developed new framework for measuring carbon emissions, \textbf{following Green Software Foundation principles}}
        \item {Lead research into carbon emissions computations that were used in the tool}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack .NET Developer} % Job title
    {HTSS} % Organization
    {Bucharest, Romania} % Location
    {Feb. 2021 - Oct. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Maintained .NET E-commerce platforms}, working mainly on performance improvements for existing use cases.}
        \item {\textbf{Added single sign-on functionality} to several linked apps, and optimized page loading >10x, by moving from eager to lazy loading.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
